
\documentclass{amsart}

\usepackage{graphicx}
%\usepackage[altbullet]{lucidabr}
%two lines below change font (font intalled manually (i.e. uploaded))
%\usepackage{fontspec}
%\setmainfont[Ligatures=TeX]{LucidaBrightRegular.ttf}
%\usepackage{kpfonts}    % for nice fonts
% option [light] for more aery documents
\usepackage{color}  %for color of references
\usepackage[dvipsnames]{xcolor} %for color of references
\usepackage{caption}
\usepackage{fancyhdr}
\usepackage[pagebackref,colorlinks, citecolor=Brown,urlcolor=Brown]{hyperref}
\usepackage{natbib}
\usepackage{multicol}
\usepackage{multirow}
%\usepackage{lscape}
\usepackage{pdflscape}
\usepackage{amssymb}
\usepackage{geometry}
\usepackage{longtable}
\usepackage{colortbl}
\usepackage{dsfont}
\usepackage{bm}
\usepackage{mathtools}
\usepackage{pgf}
\usepackage{tikz}
\usepackage{soul}
\usepackage{tikz}
\usepackage{tikz,fullpage}
\usepackage{pgf}
\usepackage{tikz}
\usetikzlibrary{shapes.geometric, arrows} %to create flow charts
\usepackage{bold-extra} %for bold small caps in the title
\usepackage{dirtree} % to create lists as tree

%\renewcommand{\familydefault}{\sfdefault} %for the sans serif font

%AMS original setup for mathematical elements
\newtheorem{theorem}{Theorem}[section]
\newtheorem{lemma}[theorem]{Lemma}
\theoremstyle{definition}
\newtheorem{definition}[theorem]{Definition}
\newtheorem{example}[theorem]{Example}
\newtheorem{xca}[theorem]{Exercise}
\theoremstyle{remark}
\newtheorem{remark}[theorem]{Remark}
\numberwithin{equation}{section}

%    Absolute value notation
\newcommand{\abs}[1]{\lvert#1\rvert}

%    Blank box placeholder for figures (to avoid requiring any
%    particular graphics capabilities for printing this document).
\newcommand{\blankbox}[2]{%
  \parbox{\columnwidth}{\centering
%    Set fboxsep to 0 so that the actual size of the box will match the
%    given measurements more closely.
    \setlength{\fboxsep}{0pt}%
    \fbox{\raisebox{0pt}[#2]{\hspace{#1}}}%
  }%
}

%Tikz setup for a flow chart
\tikzstyle{modelblock} = [rectangle, rounded corners, minimum width=3cm, minimum height=1cm,text centered, draw=black, fill=white, text ragged]

\tikzstyle{arrow} = [thick,->,>=stealth]

\begin{document}

\title{MRes Paper Draft}

%    Information for first author
\author{Arnaud Dy\`evre}
%\address{}
%\curraddr{}
%\email{a.dyevre@lse.ac.uk}
%\thanks{}

%    Information for second author
%\author{}
%\address{}
%\email{}
%\thanks{}

%    General info
%\subjclass[2000]{}

\date{\today. First created October 19, 2019}

%\dedicatory{}
%\keywords{}

%\begin{abstract}

%\end{abstract}

\maketitle

\begin{center}
     Preliminary and incomplete -- Not for sharing
\end{center}


\vspace{12pt}

%% The correct journal style for \specialsection is all uppercase; a known bug
%% in amsart.cls prevents this, so input must be uppercase until it is fixed.
%\specialsection*{This is a Special Section Head}
%\specialsection*{THIS IS A SPECIAL SECTION HEAD}
%This is an example of a special section head%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\footnote{Here is an example of a footnote. Notice that this footnote text is running on so that it can stand as an example of how a footnote with separate paragraphs should be written.
%\par
%And here is the beginning of the second paragraph.}%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


\tableofcontents

\newpage

\section{Literature review}

\cite{magerman2016heterogeneous} build a model of heterogeneous firms interlinked in a production network. They calibrate the model using the universe of firm-to-firm transactions in Belgium and conclude that two key aspects of micro-level heterogeneity lead to macro fluctuations: asymmetries in buyer-supplier linkages and share of sales going to final consumption. The relative contribution of each channel depends on the labour share in the economy. Uses monopolistic competition \textit{à la} Melitz (2003) and propagation of shocks on static networks \textit{à la} Acemoglu. There is however no dynamic network formation aspect to this model. \\

\cite{baqaee2017productivity} derive formulas for the spread of inefficiencies in a production network. They note that Hulten's theorem \citep{hulten1978growth} is the benchmark result in the recent literature on production networks. It builds on the fact that firms are cost-minimisers, they can thus leverage micro envelope conditions, instead of macro ones, as Hulten does. Changes in TFP can be decomposed as changes in pure, exogenous changes in technology and endogenous changes in allocative efficiency. Their work is related to mine but takes the view of the production network as static, uses coarse data, and is mostly interested in the decomposition of changes in GDP into allocative and technology shocks. The other problem of the paper is that they use sectoral data for input-output linkages. Lastly, their theoretical results do not deal with firm dynamics, and they do not come up with a theoretical foundation for why wedges exist in the first place (they are taken as parameters). All the results in the paper are comparative statics showing how the original level of output varies as a response to shocks in productivities and wedges. They provide a nice example of double-marginalisation and how that makes Hulten's theorem break (2.4. Example of a vertical economy).\\

\cite{baqaee2017productivity} derive a formula for the impact of a change in markups on factor shares. See appendix J.3 of their paper for an application with Cobb-Douglas production functions.\\

I need to be clear about the role of elasticities of substitutions between different producers as emphasised in the Baqaee paper. These quantities pop up all the time. \\

\section{Data}

Statistics on the universe of Belgian firms can be used to compare the \textit{Compustat} coverage \citep{magerman2016heterogeneous}.

\section{Theory}
\label{sec:theory}

\cite{magerman2016heterogeneous} use a fixed network for the theoretical and empirical exercises. But using a smaller time span than me, and not interested in the long-term evolution of the network. Also consider that extensive margin does not matter compare to intensive margin when considering spread of shocks. \\

But here, I do not care about the spread of shocks. Mostly concerned with the evolution of the network.\\

The theory will need to show the decomposition in GDP changes into changes in allocative efficiency and change in technology.\\

A nice property of the paper would be to deal with arbitrary production functions (not only Cobb-Douglas).\\

Just like \cite{baqaee2017productivity}, I need to define firms as cost minimising. This makes the mapping to the data (and the estimation of markups) consistent with the theory.

\section{Empirical exercise: the compounding effect of markups}
\label{sec:empirics}


\section{Welfare analysis}

Use model and estimates of efficiency losses from sections \ref{sec:theory} and \ref{sec:empirics} to generalise the welfare losses in the US economy, compared to what a social planner could have achieved.

\newpage

\bibliographystyle{ecta}
\bibliography{mres_paper}

\end{document}

%------------------------------------------------------------------------------
% End of journal.tex
%------------------------------------------------------------------------------
